Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-25 paper.tex

\begin{table}
% \begin{footnotesize}
\begin{tabular}{lllrl}
\toprule
{} &              parent\_lineages &          pango\_parents &   n &
descendant\_lineages \\
lineage &                              &                        &     &
\\
\midrule
XA      &        [B.1.177.18, B.1.1.7] &     [B.1.1.7, B.1.177] &   5 &
\{'XA': 5\} \\
XAA     &               [BA.1, BA.2.9] &         [BA.1*, BA.2*] &   8 &
\{'XAB': 39, 'XAG': 17, 'XAA': 8, 'XQ': 2, 'XU'... \\
XAC     &          [BA.2.3, BA.1.17.2] &  [BA.2*, BA.1*, BA.2*] &  27 &
\{'XAC': 27\} \\
XAE     &                 [BA.2, BA.1] &         [BA.2*, BA.1*] &   9 &
\{'XAE': 9\} \\
XAG     &               [BA.1, BA.2.9] &         [BA.1*, BA.2*] &  17 &
\{'XAB': 39, 'XAG': 17, 'XAA': 8, 'XQ': 2, 'XU'... \\
XF      &                 [AY.4, BA.1] &    [B.1.617.2*, BA.1*] &   2 &
\{'XF': 2\} \\
XG      &              [BA.1.17, BA.2] &         [BA.1*, BA.2*] &  32 &
\{'XG': 32, 'XAB': 1\} \\
XH      &            [BA.1.20, BA.2.9] &         [BA.1*, BA.2*] &  11 &
\{'XAF': 34, 'XH': 11, 'B.1.1.529': 3, 'XE': 3,... \\
XK      &             [BA.1.1.1, BA.2] &         [BA.1*, BA.2*] &   6 &
\{'XK': 3\} \\
XL      &            [BA.1.17.2, BA.2] &         [BA.1*, BA.2*] &  10 &
\{'XL': 10, 'XAB': 1, 'XU': 1, 'XQ': 1\} \\
XR      &               [BA.1.1, BA.2] &       [BA.1.1*, BA.2*] &   8 &
\{'XQ': 9, 'XR': 8, 'XAB': 2\} \\
XS      &              [AY.36, BA.1.1] &  [B.1.617.2*, BA.1.1*] &   6 &
\{'XS': 4\} \\
XT      &       [BA.2.23, Unknown (R)] &         [BA.2*, BA.1*] &   1 &
\{'BA.2': 1, 'BA.1': 1, 'BA.1.9': 1, 'BA.2.23':... \\
XV      &  [BA.1.1, BA.2, Unknown (R)] &         [BA.1*, BA.2*] &   3 &
\{'BA.2': 8, 'XV': 1\} \\
XW      &            [BA.1.1.15, BA.2] &         [BA.1*, BA.2*] &  11 &
\{'XW': 11, 'XN': 2\} \\
XY      &               [BA.1.1, BA.2] &         [BA.1*, BA.2*] &   6 &
\{'XY': 6, 'XAF': 1\} \\
\bottomrule
\end{tabular}
\caption{\label{tab:pango-single-origin}
Table summarising the status of the Pango X-lineages in the Long ARG that are inferred to have a single recombinant origin based on the NextClade Pango lineage assignments. Imputed parent lineages are shown from the ARG and also to parent lineages as defined by the official Pango designation alias key. FIXME: if we like this table then we can reformat it so that lists at the end are spread over multiple lines rather than using Python dict notation }
\end{table}

>>>>

\begin{table}
% \begin{footnotesize}
\begin{tabular}{lllrl}
\toprule
{} &              parent\_lineages &          pango\_parents &   n &
descendant\_lineages \\
lineage &                              &                        &     &
\\
\midrule
XA      &        [B.1.177.18, B.1.1.7] &     [B.1.1.7, B.1.177] &   5 & XA: 5 \\
XAA     &               [BA.1, BA.2.9] &         [BA.1*, BA.2*] &   8 &
    XAB: 39, XAG: 17, XAA: 8 \\
    &&&&   XAA: 8, XQ: 2, XU: ... \\
XAC     &          [BA.2.3, BA.1.17.2] &  [BA.2*, BA.1*, BA.2*] &  27 & XAC: 27 \\
XAE     &                 [BA.2, BA.1] &         [BA.2*, BA.1*] &   9 & XAE: 9 \\
XAG     &               [BA.1, BA.2.9] &         [BA.1*, BA.2*] &  17 &
    XAB: 39, XAG: 17, XAA: 8 \\
    &&&&   XAA: 8, XQ: 2, XU: ... \\
XF      &                 [AY.4, BA.1] &    [B.1.617.2*, BA.1*] &   2 & XF: 2 \\
XG      &              [BA.1.17, BA.2] &         [BA.1*, BA.2*] &  32 & XG: 32, XAB: 1 \\
XH      &            [BA.1.20, BA.2.9] &         [BA.1*, BA.2*] &  11 &
    XAF: 34, XH: 11 \\
&&&& B.1.1.529: 3, XE: 3,... \\
XK      &             [BA.1.1.1, BA.2] &         [BA.1*, BA.2*] &   6 & XK: 3 \\
XL      &            [BA.1.17.2, BA.2] &         [BA.1*, BA.2*] &  10 &
    XL: 10, XAB: 1, XU: 1, \\
    &&&& XQ: 1 \\
XR      &               [BA.1.1, BA.2] &       [BA.1.1*, BA.2*] &   8 &
    XQ: 9, XR: 8, XAB: 2\\
XS      &              [AY.36, BA.1.1] &  [B.1.617.2*, BA.1.1*] &   6 & XS: 4\\
XT      &       [BA.2.23, Unknown (R)] &         [BA.2*, BA.1*] &   1 &
    BA.2: 1, BA.1: 1, BA.1.9: 1, \\
    &&&& BA.2.23:... \\
XV      &  [BA.1.1, BA.2, Unknown (R)] &         [BA.1*, BA.2*] &   3 & BA.2: 8, XV: 1 \\
XW      &            [BA.1.1.15, BA.2] &         [BA.1*, BA.2*] &  11 & XW: 11, XN: 2 \\
XY      &               [BA.1.1, BA.2] &         [BA.1*, BA.2*] &   6 & XY: 6, XAF: 1 \\
\bottomrule
\end{tabular}
\caption{\label{tab:pango-single-origin}
Table summarising the status of the Pango X-lineages in the Long ARG thare inferred to have a single recombinant origin based on the NextClade Pango lineage assignments. Imputed parent lineages are shown from the ARG and also to parent lineages as defined by the official Pango designation alias key. FIXME: if we like this table then we can reformat it so that lists at the end are spread over multiple lines rather than using Python dict notation }
\end{table}
